---
title: "2D AR1 random effects on NAA vs. M (+CPI)"
output:
  html_document:
    df_print: paged
    self_contained: no
---

```{r setup, include=FALSE, cache = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi=300, dev = 'png', fig.align = 'center')
library(here)
library(wham)
library(tidyverse)
# devtools::load_all("/home/bstock/Documents/wham")
# library(kableExtra)
library(knitr)
library(ggsci)
library(data.table)
```

## Methods changes from Haikun's draft

- Updated population data through 2018. Use 2019 assessment with a couple modifications:
    - remove larval survey (indices 4 and 5)
    - use logistic selectivity except for blocks 1, 3, and 9 (age-specific with sel for older ages fixed at 1, as in assessment, facilitates convergence)
    - age compositions: logistic normal pool obs (wham option 5)
- Updated CPI from Chris Melrose (1972-2018)
- Added analysis comparing putting 2D AR1 devs on NAA vs. M (motivated by [Aldrin et al. 2020](https://www.sciencedirect.com/science/article/pii/S0165783620301028))

---

## Results summary (i.e. points to make in paper)

Base model has large retros ($\rho_R > 5$, $\rho_{SSB} = 1$, $\rho_F = -0.4$). Recruitment has been very poor in the period since Haikun's data ended (2012-2018), so models that do not allow temporal changes in R greatly overestimate it. Looking back at Haikun's figures, the outlook for the stock was much rosier with data ending in 2011. It has tanked since then.

1. 2D AR1 structure on random effects is useful (lower AIC and $\rho$).
    a. **NAA only**. Adding random effect deviations on NAA improves AIC and $\rho$. **2D AR1 best**. $\rho_R = 0.56$, $\rho_{SSB} = 0.09$, $\rho_F = -0.03$.
    b. **M only**. NAA devs are kind of like M devs (not really... but that's advocated by [Aldrin et al. 2020](https://www.sciencedirect.com/science/article/pii/S0165783620301028)). Adding devs on M instead of NAA also improves AIC and $\rho$. **2D AR1 best** again. Not obvious whether to estimate (higher) mean M or not: lower AIC but higher $\rho$. Just estimating $\mu_M$ without any random effects reduces AIC and $\rho$ a lot.
    c. **NAA + M**. Adding devs on both NAA and M further improves AIC and $\rho$. Gets to $\rho_R = -0.21$, $\rho_{SSB} = 0.03$, $\rho_F = 0.05$. Model with *2D AR1 on both doesn't converge*, need to have IID devs on either NAA, M, or both.

2. Environmental effect on recruitment further improves AIC and $\rho$.
    a. **NAA + CPI**. Reduces $\rho_R$ by about 0.06-0.1 compared to *NAA only*. Little change in $\rho_{SSB}$ or $\rho_F$.
    b. **NAA + M + CPI**. Consistent improvements as from adding M devs and CPI in isolation. Best model: NAA (IID) + M (2D AR1) + CPI (AR1). $\rho_R = -0.11$, $\rho_{SSB} = 0.02$, $\rho_F = 0.06$.

3. (minor) Bias correction of lognormal observations (aggregated catch and indices) slightly (but consistently) improves -logL and $\rho$.

---

## Tables

`Converged` = converged with positive definite Hessian. Model in each table with **lowest retro (not AIC)** is highlighted in grey and plotted in the figures.

#### Table 1. NAA only (models where only NAA are random effects)

Model `m1`, `NAA_sigma = rec` + `NAA_cor = iid`, estimates recruitment as independent random effects with $\sigma_R$. This is closest to a SCAA model and referred to as the "base" model in figures. `NAA_sigma = rec` + `NAA_cor = ar1_y` estimates recruitment as correlated random effects (AR1 by year). `NAA_sigma = rec+1` is the 'full state-space' model with all numbers-at-age as random effects, one $\sigma_R$ for age-1 and one $\sigma_a$ for all other ages. Models `m3`-`m6` are the four in Haikun's draft.

```{r}
df.mods <- data.frame(NAA_cor = c('iid','ar1_y','iid','ar1_a','ar1_y','2dar1'),
                      NAA_sigma = c('rec','rec','rec+1','rec+1','rec+1','rec+1'), stringsAsFactors=FALSE)
n.mods <- dim(df.mods)[1]
df.mods$Model <- paste0("m",1:n.mods)
df.mods <- df.mods %>% select(Model, everything()) # moves Model to first col

# load models
mod.list <- here("results","dat_2019","bias_correct_oe","NAA",paste0(df.mods$Model,".rds"))
mods <- lapply(mod.list, readRDS)

# calc results table
opt_conv = 1-sapply(mods, function(x) x$opt$convergence)
ok_sdrep = sapply(mods, function(x) if(x$na_sdrep==FALSE & !is.na(x$na_sdrep)) 1 else 0)
df.mods$conv <- as.logical(opt_conv)
df.mods$pdHess <- as.logical(ok_sdrep)
df.mods$runtime <- sapply(mods, function(x) x$runtime)
df.mods$NLL <- sapply(mods, function(x) round(x$opt$objective,3))
df.aic <- as.data.frame(compare_wham_models(mods, sort=FALSE, calc.rho=T, do.print=F)$tab)
df.aic$AIC[df.mods$pdHess==FALSE] <- NA
minAIC <- min(df.aic$AIC, na.rm=T)
df.aic$dAIC <- round(df.aic$AIC - minAIC,1)
df.mods <- cbind(df.mods, df.aic)
rownames(df.mods) <- NULL

df.mods$Model <- paste0("NAA-",1:6)
tochar <- function(vec2){
  if(sum(vec2)==0){
    x <- "---"
  } else {
    x <- paste0(format(round(vec2[1],2), nsmall=2), " (", format(round(vec2[2],2), nsmall=2),")")
  }
  return(x)
}
naasig <- lapply(mods, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="NAA_sigma",], ncol=2))
df.mods$sig_R <- sapply(naasig, function(x) tochar(x[1,]))
df.mods$sig_a <- c("---","---",sapply(naasig[3:6], function(x) tochar(x[2,])))
naarho_y <- lapply(mods, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="NAA_rho_y",], ncol=2))
df.mods$rho_y <- sapply(naarho_y, function(x) tochar(x[1,]))
naarho_a <- lapply(mods, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="NAA_rho_a",], ncol=2))
df.mods$rho_a <- sapply(naarho_a, function(x) tochar(x[1,]))

# dplyr::recode(df.mods$Model, m1="NAA-1", m2="NAA-2", m3="NAA-3", m4="NAA-4", m5="NAA-5", m6="NAA-6")
# df.mods$NAA_cor <- c("---","$\\rho_{y}$","---","$\\rho_{a}$","$\\rho_{y}$","$\\rho_{a}, \\rho_{y}$")
# df.mods$NAA_sigma <- c("$\\sigma_{R}$","$\\sigma_{R}$","$\\sigma_{R}, \\sigma_{a}$","$\\sigma_{R}, \\sigma_{a}$","$\\sigma_{R}, \\sigma_{a}$","$\\sigma_{R}, \\sigma_{a}$")
df.mods <- within(df.mods, rm(NAA_cor,NAA_sigma,conv,runtime,pdHess))
df.mods <- df.mods[,c(1,8:11,2,4,3,5:7)]

# posdef = which(vign6_res$pdHess == TRUE)
thebest = which(df.mods$dAIC == 0)
df.mods %>%
  # select(-one_of("pdHess")) %>% 
  # dplyr::rename("Variance\nparameters"="NAA_sigma", "Correlation\nparameters"="NAA_cor", "$\\Delta AIC$"="dAIC",  
  #              # "Converged"="conv", "Runtime\n(min)"="runtime", 
  #               "-log$(\\mathcal{L})$"="NLL","$\\rho_{R}$"="rho_R", "$\\rho_{SSB}$"="rho_SSB", "$\\rho_{\\overline{F}}$"="rho_Fbar") %>%
  dplyr::rename("$\\sigma_R$"="sig_R", "$\\sigma_a$"="sig_a", 
               "$\\rho_{year}$"="rho_y", "$\\rho_{age}$"="rho_a",
               # "Converged"="conv", "Runtime\n(min)"="runtime", 
               "$\\Delta AIC$"="dAIC", "-log$(\\mathcal{L})$"="NLL",
               # "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{\\overline{F}}$"="rho_Fbar") %>%
               "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{F}$"="rho_Fbar") %>%
  kable(escape = F)
  # kable(escape = F) %>%
  # kable_styling(bootstrap_options = c("condensed","responsive"))
  # kable_styling(bootstrap_options = c("condensed","responsive")) %>%
  # row_spec(thebest, background = gray.colors(10,end=0.95)[10])
  # row_spec(thebest, background = gray.colors(10,end=0.95)[10]) %>%
  # row_spec(thebest, bold=TRUE)
```

---

#### Table 2. M only (models where only M is a random effect)

NAA as in `m1` above (base model $\approx$ SCAA, NOT "full state-space"). Just estimating $\mu_M$, without any random effects on NAA or M, reduces AIC and $\rho$ a lot (compare `m1` to `m6`).

```{r}
df.mods <- data.frame(M_re = rep(c('none','iid','ar1_a','ar1_y','2dar1'),2),
                      est_M = rep(c(FALSE,TRUE),each=5), stringsAsFactors=FALSE)
n.mods <- dim(df.mods)[1]
df.mods$Model <- paste0("m",1:n.mods)
df.mods <- df.mods %>% select(Model, everything()) # moves Model to first col

# load models
mod.list <- here("results","dat_2019","bias_correct_oe","M",paste0(df.mods$Model,".rds"))
mods <- lapply(mod.list, readRDS)

# calc results table
opt_conv = 1-sapply(mods, function(x) x$opt$convergence)
ok_sdrep = sapply(mods, function(x) if(x$na_sdrep==FALSE & !is.na(x$na_sdrep)) 1 else 0)
df.mods$conv <- as.logical(opt_conv)
df.mods$pdHess <- as.logical(ok_sdrep)
df.mods$runtime <- sapply(mods, function(x) x$runtime)
df.mods$NLL <- sapply(mods, function(x) round(x$opt$objective,3))
df.aic <- as.data.frame(compare_wham_models(mods, sort=FALSE, calc.rho=T, do.print=F)$tab)
df.aic$AIC[df.mods$pdHess==FALSE] <- NA
minAIC <- min(df.aic$AIC, na.rm=T)
df.aic$dAIC <- round(df.aic$AIC - minAIC,1)
df.mods <- cbind(df.mods, df.aic)
rownames(df.mods) <- NULL

df.mods$Model <- paste0("M-",1:n.mods)
tochar <- function(x){
  if(!is.null(x)){
    if(nrow(x)==0){
      y <- "---"
    } else {
      if(sum(x)==0){
        y <- "---"
      } else {
        if(x[,2] == 0){
          y <- "---"
          # y <- paste0(format(round(x[1],2), nsmall=2))
        } else {
          y <- paste0(format(round(x[1],2), nsmall=2), " (", format(round(x[2],2), nsmall=2),")")
        }
      }
    }
  } else {
    y <- "*"
  }
  return(y)
}

meanM <- lapply(mods, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="mean_M",], ncol=2))
df.mods$meanM <- sapply(meanM, function(x) tochar(x))
sigM <- lapply(mods, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="sigma_M",], ncol=2))
df.mods$sigM <- sapply(sigM, function(x) tochar(x))
Mrho_y <- lapply(mods, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="rho_M_y",], ncol=2))
df.mods$rho_y <- sapply(Mrho_y, function(x) tochar(x))
Mrho_a <- lapply(mods, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="rho_M_a",], ncol=2))
df.mods$rho_a <- sapply(Mrho_a, function(x) tochar(x))

df.mods <- within(df.mods, rm(M_re,est_M,conv,runtime,pdHess))
df.mods <- df.mods[,c(1,8:11,2,4,3,5:7)]

# thebest = which(df.mods$dAIC == 0)
# thebest = c(5,10)
# thebest = 5
df.mods %>%
  # select(-one_of("pdHess")) %>% 
  dplyr::rename("$\\sigma_M$"="sigM", "$\\mu_M$"="meanM", 
               "$\\rho_{year}$"="rho_y", "$\\rho_{age}$"="rho_a",
               # "Converged"="conv", "Runtime\n(min)"="runtime", 
               "$\\Delta AIC$"="dAIC", "-log$(\\mathcal{L})$"="NLL",
               # "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{\\overline{F}}$"="rho_Fbar") %>%
               "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{F}$"="rho_Fbar") %>%
  kable(escape = F)
  # kable(escape = F) %>%
  # kable_styling(bootstrap_options = c("condensed","responsive"))
  # kable_styling(bootstrap_options = c("condensed","responsive")) %>%
  # row_spec(thebest, background = gray.colors(10,end=0.95)[10])
  # row_spec(thebest, background = gray.colors(10,end=0.95)[10]) %>%
  # row_spec(thebest, bold=TRUE)
```

---

#### Table 3. NAA + M.

```{r}
df.mods1 <- data.frame(M_re = rep(c('none','iid','ar1_a','ar1_y','2dar1'),2),
                      est_M = rep(c(FALSE,TRUE),each=5), stringsAsFactors=FALSE)
n.mods <- dim(df.mods1)[1]
df.mods1$Model <- paste0("m",1:n.mods)
df.mods1$NAA_re <- "2dar1"
df.mods1 <- df.mods1 %>% select(Model, NAA_re, everything()) %>% filter(M_re %in% c("iid","2dar1"))

# load models
mod.list <- here("results","dat_2019","bias_correct_oe","NAA_M",paste0(df.mods1$Model,".rds"))
mods1 <- lapply(mod.list, readRDS)

tochar <- function(x){
  if(is.null(x)){
    y <- "*"
    return(y)
  } else {
    if(!is.null(x)){
      x <- matrix(x, ncol=2)
      if(nrow(x)==0){
        y <- "---"
      } else {
        if(sum(x)==0){
          y <- "---"
        } else {
          if(x[,2] == 0){
            y <- "---"
            # y <- paste0(format(round(x[1],2), nsmall=2))
          } else {
            y <- paste0(format(round(x[1],2), nsmall=2), " (", format(round(x[2],2), nsmall=2),")")
          }
        }
      }
    }
  }
  return(y)
}
extract_sdrep <- function(mod, var){
  if(mod$is_sdrep) if(!mod$na_sdrep){
      matrix(summary(mod$sdrep)[rownames(summary(mod$sdrep))==var,], ncol=2)
  } else {
    y <- NULL
  }
}

# # get NAA_re par estimates
# # naasig <- lapply(mods1, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="NAA_sigma",], ncol=2))
# naasig <- lapply(mods1, extract_sdrep, "NAA_sigma")
# # naarho_y <- lapply(mods1, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="NAA_rho_y",], ncol=2))
# naarho_y <- lapply(mods1, extract_sdrep, "NAA_rho_y")
# # naarho_a <- lapply(mods1, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="NAA_rho_a",], ncol=2))
# naarho_a <- lapply(mods1, extract_sdrep, "NAA_rho_a")
# df.mods1$sig_R <- sapply(naasig, function(x) tochar(x[1,]))
# df.mods1$sig_a <- sapply(naasig, function(x) tochar(x[2,]))
# df.mods1$rho_y <- sapply(naarho_y, function(x) tochar(x))
# df.mods1$rho_a <- sapply(naarho_a, function(x) tochar(x))
# 
# # get M_re par estimates
# meanM <- lapply(mods1, extract_sdrep, "mean_M")
# sigM <- lapply(mods1, extract_sdrep, "sigma_M")
# Mrho_y <- lapply(mods1, extract_sdrep, "rho_M_y")
# Mrho_a <- lapply(mods1, extract_sdrep, "rho_M_a")
# # meanM <- lapply(mods1, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="mean_M",], ncol=2))
# df.mods1$meanM <- sapply(meanM, function(x) tochar(x))
# # sigM <- lapply(mods1, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="sigma_M",], ncol=2))
# df.mods1$sigM <- sapply(sigM, function(x) tochar(x))
# # Mrho_y <- lapply(mods1, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="rho_M_y",], ncol=2))
# df.mods1$Mrho_y <- sapply(Mrho_y, function(x) tochar(x))
# # Mrho_a <- lapply(mods1, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="rho_M_a",], ncol=2))
# df.mods1$Mrho_a <- sapply(Mrho_a, function(x) tochar(x))
# 
# # correct * vs. ---
# df.mods1$meanM[2] = "---"
# df.mods1$Mrho_y[3] = df.mods1$Mrho_a[3] = "---"

# calc results table
opt_conv = 1-sapply(mods1, function(x) x$opt$convergence)
ok_sdrep = sapply(mods1, function(x) if(x$na_sdrep==FALSE & !is.na(x$na_sdrep)) 1 else 0)
df.mods1$conv <- as.logical(opt_conv)
df.mods1$pdHess <- as.logical(ok_sdrep)
df.mods1$runtime <- sapply(mods1, function(x) x$runtime)
df.mods1$NLL <- sapply(mods1, function(x) round(x$opt$objective,3))
df.aic <- as.data.frame(compare_wham_models(mods1, sort=FALSE, calc.rho=T, do.print=F)$tab)
df.aic$AIC[df.mods1$pdHess==FALSE] <- NA
minAIC <- min(df.aic$AIC, na.rm=T)
df.aic$dAIC <- round(df.aic$AIC - minAIC,1)
df.mods1 <- cbind(df.mods1, df.aic)
rownames(df.mods1) <- NULL

# --------------------------------------------------------------------------------------------
df.mods2 <- data.frame(M_re = rep(c('none','iid','ar1_a','ar1_y','2dar1'),2),
                      est_M = rep(c(FALSE,TRUE),each=5), stringsAsFactors=FALSE)
n.mods <- dim(df.mods2)[1]
df.mods2$Model <- paste0("m",1:n.mods)
df.mods2$NAA_re <- "iid"
df.mods2 <- df.mods2 %>% select(Model, NAA_re, everything()) %>% filter(M_re %in% c("iid","2dar1"))

# load models
mod.list <- here("results","dat_2019","bias_correct_oe","NAA_M_iid",paste0(df.mods2$Model,".rds"))
mods2 <- lapply(mod.list, readRDS)

# # get NAA_re par estimates
# naasig <- lapply(mods2, extract_sdrep, "NAA_sigma")
# naarho_y <- lapply(mods2, extract_sdrep, "NAA_rho_y")
# naarho_a <- lapply(mods2, extract_sdrep, "NAA_rho_a")
# df.mods2$sig_R <- sapply(naasig, function(x) tochar(x[1,]))
# df.mods2$sig_a <- sapply(naasig, function(x) tochar(x[2,]))
# df.mods2$rho_y <- sapply(naarho_y, function(x) tochar(x))
# df.mods2$rho_a <- sapply(naarho_a, function(x) tochar(x))
# 
# # get M_re par estimates
# meanM <- lapply(mods2, extract_sdrep, "mean_M")
# sigM <- lapply(mods2, extract_sdrep, "sigma_M")
# Mrho_y <- lapply(mods2, extract_sdrep, "rho_M_y")
# Mrho_a <- lapply(mods2, extract_sdrep, "rho_M_a")
# df.mods2$meanM <- sapply(meanM, function(x) tochar(x))
# df.mods2$sigM <- sapply(sigM, function(x) tochar(x))
# df.mods2$Mrho_y <- sapply(Mrho_y, function(x) tochar(x))
# df.mods2$Mrho_a <- sapply(Mrho_a, function(x) tochar(x))
# 
# # correct * vs. ---
# df.mods2$rho_y[3] = df.mods2$rho_a[3] = "---"
# df.mods2$meanM[2] = "---"
# df.mods2$Mrho_y[3] = df.mods2$Mrho_a[3] = "---"

# calc results table
opt_conv = 1-sapply(mods2, function(x) x$opt$convergence)
ok_sdrep = sapply(mods2, function(x) if(x$na_sdrep==FALSE & !is.na(x$na_sdrep)) 1 else 0)
df.mods2$conv <- as.logical(opt_conv)
df.mods2$pdHess <- as.logical(ok_sdrep)
df.mods2$runtime <- sapply(mods2, function(x) x$runtime)
df.mods2$NLL <- sapply(mods2, function(x) round(x$opt$objective,3))
df.aic <- as.data.frame(compare_wham_models(mods2, sort=FALSE, calc.rho=T, do.print=F)$tab)
df.aic$AIC[df.mods2$pdHess==FALSE] <- NA
minAIC <- min(df.aic$AIC, na.rm=T)
df.aic$dAIC <- round(df.aic$AIC - minAIC,1)
df.mods2 <- cbind(df.mods2, df.aic)
rownames(df.mods2) <- NULL

# -----------------------------------------------------------
# combine two tables
df.mods <- rbind(df.mods2, df.mods1)
df.mods$Model <- paste0("NAA-M-",1:dim(df.mods)[1])
df.mods[df.mods$pdHess==FALSE, c("NLL","dAIC","AIC","rho_R","rho_SSB","rho_Fbar")] = NA
minAIC <- min(df.mods$AIC, na.rm=T)
df.mods$dAIC <- df.mods$AIC - minAIC
# df.mods <- within(df.mods, rm(NAA_re,M_re,est_M,conv,runtime,pdHess))
df.mods <- within(df.mods, rm(conv,runtime,pdHess))
# df.mods <- df.mods[,c(1,8:11,2,4,3,5:7)]
df.mods$NLL <- paste0(format(round(df.mods$NLL,3), nsmall=3))
df.mods$dAIC <- paste0(format(round(df.mods$dAIC,1), nsmall=1))
df.mods[is.na(df.mods)] = ""
df.mods[df.mods == "       NA"] = ""
df.mods[df.mods == "  NA"] = ""
df.mods[df.mods == "iid"] = "IID"
df.mods[df.mods == "2dar1"] = "2D AR1"
df.mods[df.mods == FALSE] = "No"
df.mods[df.mods == TRUE] = "Yes"
df.mods <- df.mods[,c(1:5,7,6,8:10)]

# thebest = which(df.mods$dAIC == 0)
# thebest = c(2,5)
# thebest = 2
df.mods %>%
  # select(-one_of("pdHess")) %>% 
  # dplyr::rename("$\\sigma_R$"="sig_R", "$\\sigma_a$"="sig_a", 
  #              "$\\rho_{year}$"="rho_y", "$\\rho_{age}$"="rho_a",
  #              "$\\sigma_M$"="sigM", "$\\mu_M$"="meanM", 
  #              "$\\rho^M_{year}$"="Mrho_y", "$\\rho^M_{age}$"="Mrho_a",
  #              # "Converged"="conv", "Runtime\n(min)"="runtime", 
  #              "$\\Delta AIC$"="dAIC", "-log$(\\mathcal{L})$"="NLL",
  #              "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{\\overline{F}}$"="rho_Fbar") %>%
  # dplyr::rename("Estimate $\\mu_{M}$"="est_M","Random effects\nNAA"="NAA_re","Random effects\nM"="M_re",
  #              "$\\Delta AIC$"="dAIC", "-log$(\\mathcal{L})$"="NLL",
  #              "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{\\overline{F}}$"="rho_Fbar") %>%
  # dplyr::rename("Estimate $\\mu_{M}$"="est_M","Random effects\nNAA"="NAA_re","Random effects\nM"="M_re",
  #              "$\\Delta AIC$"="dAIC", "-log$(\\mathcal{L})$"="NLL",
  #              "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{F}$"="rho_Fbar") %>%
  dplyr::rename("Estimate $\\mu_{M}$"="est_M","Random effects NAA"="NAA_re","Random effects M"="M_re",
               "$\\Delta AIC$"="dAIC", "-log$(\\mathcal{L})$"="NLL",
               "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{F}$"="rho_Fbar") %>%
  kable(escape = F)
  # kable(escape = F) %>%
  # kable_styling(bootstrap_options = c("condensed","responsive"))
  # kable_styling(bootstrap_options = c("condensed","responsive")) %>%
  # row_spec(thebest, background = gray.colors(10,end=0.95)[10])
  # row_spec(thebest, background = gray.colors(10,end=0.95)[10]) %>%
  # row_spec(thebest, bold=TRUE)
```

---

#### Table 4. NAA + M + CPI.

```{r}
df.mods <- data.frame(NAA_re = rep(c(rep('iid',4),rep('2dar1',4),rep('iid',4)),2),
                      M_re = rep(c(rep('iid',4),rep('iid',4),rep('2dar1',4)),2),
                      est_M = rep(c(FALSE,FALSE,TRUE,TRUE),6),
                      CPI_how = rep(rep(c(0,2),6),2),
                      CPI_mod = c(rep("rw",12),rep("ar1",12)), stringsAsFactors=FALSE)
n.mods <- dim(df.mods)[1]
df.mods$Model <- paste0("m",1:n.mods)
df.mods <- df.mods %>% select(Model, everything()) # moves Model to first col

# load models
mod.list <- here("results","dat_2019","bias_correct_oe","NAA_M_CPI",paste0(df.mods$Model,".rds"))
mods <- lapply(mod.list, readRDS)

# calc results table
opt_conv = 1-sapply(mods, function(x) x$opt$convergence)
ok_sdrep = sapply(mods, function(x) if(x$na_sdrep==FALSE & !is.na(x$na_sdrep)) 1 else 0)
df.mods$conv <- as.logical(opt_conv)
df.mods$pdHess <- as.logical(ok_sdrep)
df.mods$runtime <- sapply(mods, function(x) x$runtime)
df.mods$NLL <- sapply(mods, function(x) round(x$opt$objective,3))
have_peels <- sapply(mods, function(x) !is.null(x$peels))
df.aic <- as.data.frame(compare_wham_models(mods, sort=FALSE, calc.rho=F, do.print=F)$tab)
df.aic$dAIC <- df.aic$rho_Fbar <- df.aic$rho_SSB <- df.aic$rho_R <- NA
if(any(have_peels)){
	tmp <- as.data.frame(compare_wham_models(mods[have_peels], sort=FALSE, calc.rho=T, do.print=F)$tab)
	df.aic[have_peels==TRUE, 3:5] <- tmp[,3:5]
	df.aic[df.mods$pdHess==FALSE,] <- NA
}
minAIC <- min(df.aic$AIC, na.rm=T)
df.aic$dAIC <- round(df.aic$AIC - minAIC,1)
df.mods <- cbind(df.mods, df.aic)
rownames(df.mods) <- NULL

df <- df.mods %>% filter(NAA_re == "iid", CPI_how==2, CPI_mod=='ar1', pdHess==TRUE)
df$Model <- paste0("NAA-M-CPI-",1:dim(df)[1])
df[df == "iid"] = "IID"
df[df == "2dar1"] = "2D AR1"
df[df == FALSE] = "No"
df$dAIC[3] = "0.0"
df[df == TRUE] = "Yes"
df <- df[,c(1:10,12,11,13:15)]

# thebest = 2
df %>%
  # select(-one_of("pdHess","CPI_how","CPI_mod")) %>% 
  # dplyr::rename("Estimate $\\mu_{M}$"="est_M", "Converged"="conv", "Runtime\n(min)"="runtime", "$\\Delta AIC$"="dAIC",
  #        "$\\rho_{R}$"="rho_R", "$\\rho_{SSB}$"="rho_SSB", "$\\rho_{\\overline{F}}$"="rho_Fbar") %>%
  select(-one_of("pdHess","conv","CPI_how","CPI_mod","runtime")) %>% 
  dplyr::rename("Estimate $\\mu_{M}$"="est_M", "Random effects on NAA"="NAA_re","Random effects on M"="M_re",
         "$\\Delta AIC$"="dAIC","$\\rho_{R}$"="rho_R", "$\\rho_{SSB}$"="rho_SSB", "$\\rho_{F}$"="rho_Fbar") %>%
    # dplyr::rename("Estimate $\\mu_{M}$"="est_M", "Random effects on NAA"="NAA_re","Random effects on M"="M_re",
    #      "$\\Delta AIC$"="dAIC","$\\rho_{R}$"="rho_R", "$\\rho_{SSB}$"="rho_SSB", "$\\rho_{\\overline{F}}$"="rho_Fbar") %>%
kable(escape = F)
  # kable(escape = F) %>%
  # kable_styling(bootstrap_options = c("condensed","responsive"))
  # kable_styling(bootstrap_options = c("condensed","responsive")) %>%
  # row_spec(thebest, background = gray.colors(10,end=0.95)[10])
```

---

<!-- #### Table 5. Best models with CPI fit so can compare AIC, F=0 in projections so can compare SSB predictions. -->

<!-- ```{r} -->
<!-- df.mods <- data.frame(NAA_cor = c('iid','iid','2dar1','iid','iid','iid','2dar1','iid'), -->
<!--                       NAA_sigma = c('rec','rec+1','rec+1','rec','rec','rec+1','rec+1','rec+1'), -->
<!--                       M_re = c('none','none','none','iid','2dar1','2dar1','iid','2dar1'), -->
<!--                       CPI_how = c(rep(0,7),2), stringsAsFactors=FALSE) -->
<!-- n.mods <- dim(df.mods)[1] -->
<!-- df.mods$Model <- paste0("m",1:n.mods) -->
<!-- df.mods$lab <- c("NAA-1","NAA-3","NAA-6","M-2","M-5","NAA-M-2","NAA-M-5","NAA-M-CPI-2") -->
<!-- df.mods <- df.mods %>% select(Model, lab, everything()) # moves Model to first col -->
<!-- # M-2 wouldn't converge for some reason... remove it -->
<!-- df.mods <- filter(df.mods, Model != "m4") -->

<!-- # load models -->
<!-- mod.list <- here("results","dat_2019","bias_correct_oe","best_zeroFproj",paste0(df.mods$Model,".rds")) -->
<!-- mods <- lapply(mod.list, readRDS) -->

<!-- # calc results table -->
<!-- opt_conv = 1-sapply(mods, function(x) x$opt$convergence) -->
<!-- ok_sdrep = sapply(mods, function(x) if(x$na_sdrep==FALSE & !is.na(x$na_sdrep)) 1 else 0) -->
<!-- df.mods$conv <- as.logical(opt_conv) -->
<!-- df.mods$pdHess <- as.logical(ok_sdrep) -->
<!-- df.mods$runtime <- sapply(mods, function(x) x$runtime) -->
<!-- df.mods$NLL <- sapply(mods, function(x) round(x$opt$objective,3)) -->
<!-- have_peels <- sapply(mods, function(x) !is.null(x$peels)) -->
<!-- df.aic <- as.data.frame(compare_wham_models(mods, sort=FALSE, calc.rho=F, do.print=F)$tab) -->
<!-- df.aic$dAIC <- df.aic$rho_Fbar <- df.aic$rho_SSB <- df.aic$rho_R <- NA -->
<!-- if(any(have_peels)){ -->
<!-- 	tmp <- as.data.frame(compare_wham_models(mods[have_peels], sort=FALSE, calc.rho=T, do.print=F)$tab) -->
<!-- 	df.aic[have_peels==TRUE, 3:5] <- tmp[,3:5] -->
<!-- 	df.aic[df.mods$pdHess==FALSE,] <- NA -->
<!-- } -->
<!-- minAIC <- min(df.aic$AIC, na.rm=T) -->
<!-- df.aic$dAIC <- round(df.aic$AIC - minAIC,1) -->
<!-- df.mods <- cbind(df.mods, df.aic) -->
<!-- rownames(df.mods) <- NULL -->

<!-- df <- df.mods -->
<!-- df$Model <- df.mods$lab -->
<!-- df$CPI_how <- as.character(df$CPI_how) -->
<!-- df[df == "0"] = "---" -->
<!-- df$dAIC[df$dAIC == "---"] = "0.0" -->
<!-- df[df == "2"] = "Yes" -->
<!-- df[df == "none"] = "---" -->
<!-- df[df == "rec"] = "Recruit" -->
<!-- df[df == "rec+1"] = "All NAA" -->
<!-- df[df == "iid"] = "IID" -->
<!-- df[df == "2dar1"] = "2D AR1" -->
<!-- df[df == FALSE] = "No" -->
<!-- # df$dAIC[3] = "0.0" -->
<!-- df[df == TRUE] = "Yes" -->
<!-- # df <- df[,c(1:10,12,11,13:15)] -->

<!-- get_proj_SSB_CI <- function(mod){ -->
<!--   temp = summary(mod$sdrep) -->
<!--   temp = temp[rownames(temp) == "log_SSB",] -->
<!--   temp = exp(cbind(temp, temp[,1] + qnorm(0.975)*cbind(-temp[,2],temp[,2]))) -->
<!--   temp = cbind(temp, temp[,4] - temp[,3]) -->
<!--   temp = tail(temp,3) -->
<!--   y <- apply(temp, 1, function(x) paste0(format(round(x[1],0), nsmall=0), " (", format(round(x[3],0), nsmall=0),", ",format(round(x[4],0), nsmall=0),")")) -->
<!--   names(y) = NULL -->
<!--   return(y) -->
<!-- } -->
<!-- proj.SSB <- lapply(mods, get_proj_SSB_CI) -->
<!-- ssb.df <- do.call(rbind, proj.SSB) -->
<!-- df <- cbind(df, ssb.df) -->
<!-- colnames(df)[16:18] <- c("2019","2020","2021") -->

<!-- df %>% -->
<!--   select(-one_of("pdHess","conv","runtime","lab")) %>%  -->
<!--   dplyr::rename("CPI"="CPI_how","NAA dev"="NAA_sigma","NAA cor"="NAA_cor","Random effects on M"="M_re", -->
<!--          "$\\Delta AIC$"="dAIC","$\\rho_{R}$"="rho_R", "$\\rho_{SSB}$"="rho_SSB", "$\\rho_{F}$"="rho_Fbar") %>% -->
<!-- kable(escape = F) -->

<!-- ``` -->

## Figures

#### Fig 1. NAA devs (in models where only NAA are random effects)

```{r, fig.height = 6, fig.width = 7}
df.mods <- data.frame(NAA_cor = c('iid','ar1_y','iid','ar1_a','ar1_y','2dar1'),
                      NAA_sigma = c('rec','rec','rec+1','rec+1','rec+1','rec+1'), stringsAsFactors=FALSE)
n.mods <- dim(df.mods)[1]
df.mods$Model <- paste0("m",1:n.mods)
df.mods <- df.mods %>% select(Model, everything()) # moves Model to first col

# load models
mod.list <- here("results","dat_2019","bias_correct_oe","NAA",paste0(df.mods$Model,".rds"))
mods <- lapply(mod.list, readRDS)

df.mods$Model <- paste0("NAA-",1:n.mods)
df.mods$NAA_cor <- factor(df.mods$NAA_cor, levels=c('iid','ar1_a','ar1_y','2dar1'), labels=c("IID","AR1[age]","AR1[year]","'2D'~AR1"))
df.mods$NAA_sigma <- factor(df.mods$NAA_sigma, levels=c('rec','rec+1'), labels=c("Random~effects:~Recruitment","Random~effects:~all~NAA"))
n_ages <- mods[[1]]$env$data$n_ages
df.NAA <- data.frame(matrix(NA, nrow=0, ncol=n_ages+3))
colnames(df.NAA) <- c(paste0("Age_",1:n_ages),"Year","NAA_cor","NAA_sigma")
for(i in 1:length(mods)){
  tmp = as.data.frame(mods[[i]]$rep$NAA_devs)[1:(length(mods[[i]]$years_full)-1),]
  tmp$Year <- mods[[i]]$years_full[-1]
  colnames(tmp) <- c(paste0("Age_",1:n_ages),"Year")
  tmp$NAA_cor = df.mods$NAA_cor[i]
  tmp$NAA_sigma = df.mods$NAA_sigma[i]
  df.NAA <- rbind(df.NAA, tmp)
}
df.plot <- df.NAA %>% tidyr::pivot_longer(-c(Year,NAA_cor,NAA_sigma),
          names_to = "Age",
          names_prefix = "Age_",
          names_transform = list(Age = as.integer),
          values_to = "NAA_re")
df.plot$NAA_re[df.plot$NAA_sigma == "Random~effects:~Recruitment" & df.plot$Age > 1] = 0
df.mods$xint = tail(mods[[1]]$years,1)

print(ggplot(df.plot, ggplot2::aes(x=Year, y=Age)) +
      geom_tile(aes(fill=NAA_re)) +
      geom_label(aes(x=Year, y=Age, label=lab), size=4, alpha=1, label.r=unit(0, "lines"), label.size=NA,
          data=data.frame(Year=1978, Age=5.7, lab=df.mods$Model, NAA_cor=df.mods$NAA_cor, NAA_sigma=df.mods$NAA_sigma)) +
      geom_vline(data=df.mods, mapping=aes(xintercept = xint), linetype=2, size=.4) +
      scale_x_continuous(expand=c(0,0)) +
      scale_y_continuous(expand=c(0,0)) +
      theme_bw() +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
      facet_grid(rows=vars(NAA_cor), cols=vars(NAA_sigma), drop=F, labeller = label_parsed) +
      scale_fill_gradient2(name = "NAA devs", low = scales::muted("blue"), mid = "white", high = scales::muted("red")))
```

#### Fig 2. M devs (in models where only M is random effect)

```{r, fig.height = 6, fig.width = 7}
df.mods <- data.frame(M_re = rep(c('none','iid','ar1_a','ar1_y','2dar1'),2),
                      est_M = rep(c(FALSE,TRUE),each=5), stringsAsFactors=FALSE)
n.mods <- dim(df.mods)[1]
df.mods$Model <- paste0("m",1:n.mods)
df.mods <- df.mods %>% select(Model, everything()) # moves Model to first col

# load models
mod.list <- here("results","dat_2019","bias_correct_oe","M",paste0(df.mods$Model,".rds"))
mods <- lapply(mod.list, readRDS)

df.mods$Model <- paste0("M-",1:n.mods)
df.mods$M_re <- factor(df.mods$M_re, levels=c('none','iid','ar1_a','ar1_y','2dar1'), labels=c("None","IID","AR1[age]","AR1[year]","'2D'~AR1"))
# df.mods$est_M <- factor(df.mods$est_M, levels=c(FALSE,TRUE), labels=c("mean M fixed","mean M estimated"))
df.mods$est_M <- factor(df.mods$est_M, levels=c(FALSE,TRUE), labels=c("Fixed~mu[M]","Estimated~mu[M]"))
n_ages <- mods[[1]]$env$data$n_ages
df.NAA <- data.frame(matrix(NA, nrow=0, ncol=n_ages+3))
colnames(df.NAA) <- c(paste0("Age_",1:n_ages),"Year","M_re","est_M")
for(i in 1:length(mods)){
  tmp = as.data.frame(mods[[i]]$rep$M_re)[1:length(mods[[i]]$years_full),]
  tmp$Year <- mods[[i]]$years_full
  colnames(tmp) <- c(paste0("Age_",1:n_ages),"Year")
  tmp$M_re = df.mods$M_re[i]
  tmp$est_M = df.mods$est_M[i]
  if(i %in% c(1,3,6,8)){
    for(y in (mods[[i]]$env$data$n_years_model+1):length(mods[[i]]$years_full)){
      tmp[y,1:6] <- tmp[length(mods[[i]]$years), 1:6]
    }
  }
  df.NAA <- rbind(df.NAA, tmp)
}
df.plot <- df.NAA %>% tidyr::pivot_longer(-c(Year,M_re,est_M),
          names_to = "Age",
          names_prefix = "Age_",
          names_transform = list(Age = as.integer),
          values_to = "M_devs")
# df.plot$M_re[df.plot$est_M == "RE: Recruit" & df.plot$Age > 1] = 0

print(ggplot(df.plot, ggplot2::aes(x=Year, y=Age)) +
      geom_tile(aes(fill=M_devs)) +
      geom_vline(xintercept = tail(mods[[1]]$years,1), linetype=2, size=.4) +
      geom_label(aes(x=Year, y=Age, label=lab), size=4, alpha=1, label.r=unit(0, "lines"), label.size=NA,
          data=data.frame(Year=1976, Age=5.7, lab=df.mods$Model, M_re=df.mods$M_re, est_M=df.mods$est_M)) +
      scale_x_continuous(expand=c(0,0)) +
      scale_y_continuous(expand=c(0,0)) +
      theme_bw() +
      facet_grid(rows=vars(M_re), cols=vars(est_M), drop=F, labeller = label_parsed) +
      scale_fill_gradient2(name = "M devs", low = scales::muted("blue"), mid = "white", high = scales::muted("red")))
```


#### Fig 3. Adding CPI-Recruitment effect reduces $\rho_R$ and AIC. $\rho_{SSB}$ and $\rho_F$ unchanged.

Perhaps too much detail, could make one boxplot per rho instead. Supplement since not focus of paper?

```{r, fig.height = 3, fig.width = 6}
df.mods <- data.frame(NAA_cor = rep(c('iid','ar1_y','iid','ar1_a','ar1_y','2dar1'),4),
                      NAA_sigma = rep(c('rec','rec','rec+1','rec+1','rec+1','rec+1'),4),
                      CPI_mod = c(rep("rw",12), rep("ar1",12)),
                      CPI_how = rep(c(rep(0,6),rep(2,6)),2), stringsAsFactors=FALSE)
n.mods <- dim(df.mods)[1]
df.mods$Model <- paste0("m",1:n.mods)
df.mods <- df.mods %>% select(Model, everything()) # moves Model to first col

# load models
mod.list <- here("results","dat_2019","bias_correct_oe","NAA_CPI",paste0(df.mods$Model,".rds"))
mods <- lapply(mod.list, readRDS)

# calc results table
opt_conv = 1-sapply(mods, function(x) x$opt$convergence)
ok_sdrep = sapply(mods, function(x) if(x$na_sdrep==FALSE & !is.na(x$na_sdrep)) 1 else 0)
df.mods$conv <- as.logical(opt_conv)
df.mods$pdHess <- as.logical(ok_sdrep)
df.mods$runtime <- sapply(mods, function(x) x$runtime)
df.mods$NLL <- sapply(mods, function(x) round(x$opt$objective,3))
df.aic <- as.data.frame(compare_wham_models(mods, sort=FALSE, calc.rho=T, do.print=F)$tab)
df.aic$AIC[df.mods$pdHess==FALSE] <- NA
minAIC <- min(df.aic$AIC, na.rm=T)
df.aic$dAIC <- round(df.aic$AIC - minAIC,1)
df.mods <- cbind(df.mods, df.aic)
rownames(df.mods) <- NULL

diff <- df.mods %>% filter(NAA_sigma=="rec+1",CPI_mod=='ar1' & CPI_how==2) %>% select(rho_R,rho_SSB,rho_Fbar) %>% abs - df.mods %>% filter(NAA_sigma=="rec+1",CPI_mod=='ar1' & CPI_how==0) %>% select(rho_R,rho_SSB,rho_Fbar) %>% abs
diff$NAA_re <- c("iid","ar1_a","ar1_y","2dar1")
df1 <- diff %>% pivot_longer(-NAA_re, names_to = "var", values_to = "val")
df1$M_re <- "none"

df.mods <- data.frame(NAA_re = rep(c(rep('iid',4),rep('2dar1',4),rep('iid',4)),2),
                      M_re = rep(c(rep('iid',4),rep('iid',4),rep('2dar1',4)),2),
                      est_M = rep(c(FALSE,FALSE,TRUE,TRUE),6),
                      CPI_how = rep(rep(c(0,2),6),2),
                      CPI_mod = c(rep("rw",12),rep("ar1",12)), stringsAsFactors=FALSE)
n.mods <- dim(df.mods)[1]
df.mods$Model <- paste0("m",1:n.mods)
df.mods <- df.mods %>% select(Model, everything()) # moves Model to first col

# load models
mod.list <- here("results","dat_2019","bias_correct_oe","NAA_M_CPI",paste0(df.mods$Model,".rds"))
mods <- lapply(mod.list, readRDS)

# calc results table
opt_conv = 1-sapply(mods, function(x) x$opt$convergence)
ok_sdrep = sapply(mods, function(x) if(x$na_sdrep==FALSE & !is.na(x$na_sdrep)) 1 else 0)
df.mods$conv <- as.logical(opt_conv)
df.mods$pdHess <- as.logical(ok_sdrep)
df.mods$runtime <- sapply(mods, function(x) x$runtime)
df.mods$NLL <- sapply(mods, function(x) round(x$opt$objective,3))

	have_peels <- sapply(mods, function(x) !is.null(x$peels))
	df.aic <- as.data.frame(compare_wham_models(mods, sort=FALSE, calc.rho=F, do.print=F)$tab)
	df.aic$dAIC <- df.aic$rho_Fbar <- df.aic$rho_SSB <- df.aic$rho_R <- NA
	if(any(have_peels)){
		tmp <- as.data.frame(compare_wham_models(mods[have_peels], sort=FALSE, calc.rho=T, do.print=F)$tab)
		df.aic[have_peels==TRUE, 3:5] <- tmp[,3:5]
		df.aic[df.mods$pdHess==FALSE,] <- NA
	}

# df.aic <- as.data.frame(compare_wham_models(mods, sort=FALSE, calc.rho=T)$tab)
# df.aic$AIC[df.mods$pdHess==FALSE] <- NA
minAIC <- min(df.aic$AIC, na.rm=T)
df.aic$dAIC <- round(df.aic$AIC - minAIC,1)
df.mods <- cbind(df.mods, df.aic)
rownames(df.mods) <- NULL

diff <- df.mods %>% filter(NAA_re == "iid", CPI_how==2, CPI_mod=='ar1', pdHess==TRUE) %>% select(rho_R,rho_SSB,rho_Fbar) %>% abs - df.mods %>% filter(NAA_re == "iid", CPI_how==0, CPI_mod=='ar1', pdHess==TRUE) %>% select(rho_R,rho_SSB,rho_Fbar) %>% abs
diff$NAA_re <- "iid"
df2 <- diff %>% pivot_longer(-NAA_re, names_to = "var", values_to = "val")
df2$M_re <- c("iid / 2dar1")

df <- rbind(df1,df2)
df$var <- factor(df$var, levels=c("rho_R","rho_SSB","rho_Fbar"), labels=c("`Mohn's`~rho[R]","`Mohn's`~rho[SSB]","`Mohn's`~rho[F]"))
df$NAA_re <- factor(df$NAA_re, levels=c("iid","ar1_a","ar1_y","2dar1"), labels=c("IID","AR1[age]","AR1[year]","'2D'~AR1"))
df$M_re <- factor(df$M_re, levels=c("none","iid / 2dar1"), labels=c("None","IID / 2D AR1"))

ggplot(df, aes(x=NAA_re, y=val, fill=M_re)) +
  geom_point(pch = 21) +
  geom_hline(yintercept=0, linetype="dashed") +
  facet_wrap(vars(var), nrow=1, strip.position = "top", labeller = label_parsed) +
  ylab(expression(Reduction~"in"~"|"*"Mohn's"~rho*"|")) +
  xlab("NAA random effect structure") +
  scale_x_discrete(labels = function(l) parse(text=l)) +
  scale_fill_grey(name="M random effects") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```

#### Fig 4. NAA and M devs in final model (NAA + M + CPI random effects).

Only showing NAA + M + CPI model with lowest rho (< 0.1 for all three), even though it has higher AIC. Could show all 3 in a multipanel.

```{r, fig.height = 7, fig.width = 7}
mod <- readRDS(here("results","dat_2019","bias_correct_oe","NAA_M_CPI","m22.rds"))
n_ages <- mod$env$data$n_ages
df <- data.frame(matrix(NA, nrow=0, ncol=n_ages+2))
colnames(df) <- c(paste0("Age_",1:n_ages),"Year","type")
tmp = as.data.frame(mod$rep$M_re)[1:length(mod$years_full),]
tmp$Year <- mod$years_full
colnames(tmp) <- c(paste0("Age_",1:n_ages),"Year")
tmp$type = "log(M) deviations"
df <- rbind(df, tmp)

# add NAA devs
tmp = as.data.frame(mod$rep$NAA_devs)[1:(length(mod$years_full)-1),]
tmp$Year <- mod$years_full[-1]
colnames(tmp) <- c(paste0("Age_",1:n_ages),"Year")
tmp$type = "log(NAA) deviations"
df <- rbind(df, tmp)

df.plot <- df %>% tidyr::pivot_longer(-c(Year,type),
          names_to = "Age",
          names_prefix = "Age_",
          names_transform = list(Age = as.integer),
          values_to = "devs")

print(ggplot(df.plot, ggplot2::aes(x=Year, y=Age)) +
      geom_tile(aes(fill=devs)) +
      geom_vline(xintercept = tail(mod$years,1), linetype=2, size=.4) +
      scale_x_continuous(expand=c(0,0)) +
      scale_y_continuous(expand=c(0,0)) +
      theme_bw() +
      facet_wrap(vars(type), nrow=2, ncol=1) +
      scale_fill_gradient2(name = "", low = scales::muted("blue"), mid = "white", high = scales::muted("red")))

```


#### Fig 5. Retros for SSB and F (base, NAA, M, NAA + M, NAA + M + CPI)

```{r message=FALSE, warning=FALSE, fig.height = 5, fig.width = 8}
mod.list <- c(here("results","dat_2019","bias_correct_oe","NAA","m1.rds"),
              here("results","dat_2019","bias_correct_oe","NAA","m6.rds"),
              here("results","dat_2019","bias_correct_oe","M","m5.rds"),
              here("results","dat_2019","bias_correct_oe","NAA_M_iid","m5.rds"),
              here("results","dat_2019","bias_correct_oe","NAA_M_CPI","m22.rds"))
mods <- lapply(mod.list, readRDS)
mod.labs <- c("base","NAA", "M", "NAA + M", "NAA + M + CPI")
years = mods[[1]]$years
nyears <- length(years) # don't use projections
npeels = length(mods[[1]]$peels)
nyears.plot <- 20
nyears.cut <- nyears-nyears.plot

dfrho <- data.frame(matrix(NA, nrow=0, ncol=3))
colnames(dfrho) <- c("val","var","Model")
df <- data.frame(matrix(NA, nrow=0, ncol=5))
colnames(df) <- c("Year","peel","val","var","Model")
for(i in 1:length(mods)){
  ssb = list(head(mods[[i]]$rep[["SSB"]],nyears))
  ssb[2:(npeels+1)] = lapply(mods[[i]]$peels, function(x) x$rep[["SSB"]])
  rel.ssb = lapply(1:length(ssb), function(x) ssb[[x]]/ssb[[1]][1:(nyears - x + 1)] - 1)
  tmp <- as.data.frame(t(plyr::ldply(rel.ssb, rbind))[(nyears.cut+1):(nyears-1),])[,-1]
  colnames(tmp) <- paste0("peel",1:npeels)
  tmp$Year <- tail(years, nyears.plot-1)
  tmp <- tmp %>% tidyr::pivot_longer(-Year, names_to = "peel", names_prefix = "peel",
                              names_transform = list(peel = as.integer), values_to = "val")
  tmp$var = "SSB"
  tmp$Model = mod.labs[i]
  df <- rbind(df, tmp)
  
  Fbar = list(head(mods[[i]]$rep[["Fbar"]],nyears))
  Fbar[2:(npeels+1)] = lapply(mods[[i]]$peels, function(x) x$rep[["Fbar"]])
  rel.Fbar = lapply(1:length(Fbar), function(x) Fbar[[x]]/Fbar[[1]][1:(nyears - x + 1)] - 1)  
  tmp <- as.data.frame(t(plyr::ldply(rel.Fbar, rbind))[(nyears.cut+1):(nyears-1),])[,-1]
  colnames(tmp) <- paste0("peel",1:npeels)
  tmp$Year <- tail(years, nyears.plot-1)
  tmp <- tmp %>% tidyr::pivot_longer(-Year, names_to = "peel", names_prefix = "peel",
                              names_transform = list(peel = as.integer), values_to = "val")
  tmp$var = "F"
  tmp$Model = mod.labs[i]
  df <- rbind(df, tmp)
  
  Rec = list(head(mods[[i]]$rep[["NAA"]][,1],nyears))
  Rec[2:(npeels+1)] = lapply(mods[[i]]$peels, function(x) x$rep[["NAA"]][,1])
  rel.Rec = lapply(1:length(Rec), function(x) Rec[[x]]/Rec[[1]][1:(nyears - x + 1)] - 1)
  tmp <- as.data.frame(t(plyr::ldply(rel.Rec, rbind))[(nyears.cut+1):(nyears-1),])[,-1]
  colnames(tmp) <- paste0("peel",1:npeels)
  tmp$Year <- tail(years, nyears.plot-1)
  tmp <- tmp %>% tidyr::pivot_longer(-Year, names_to = "peel", names_prefix = "peel",
                              names_transform = list(peel = as.integer), values_to = "val")
  tmp$var = "Recruitment"
  tmp$Model = mod.labs[i]
  df <- rbind(df, tmp)

  
  dfrho <- rbind(dfrho, data.frame(val=wham::mohns_rho(mods[[i]])[1:3], var=c("SSB","F","Recruitment"), Model=mod.labs[i]))
}

dfrho$Year = as.integer(years[nyears.cut]+2)
dfrho$yval = 1.6
dfrho$val = paste0("rho == ",sprintf("%.2f",round(dfrho$val,2)))

df$Model <- factor(df$Model, levels=c("base","NAA", "M", "NAA + M", "NAA + M + CPI"), labels=c("base","NAA", "M", "NAA + M", "NAA + M + CPI"))
dfrho$Model <- factor(dfrho$Model, levels=c("base","NAA", "M", "NAA + M", "NAA + M + CPI"), labels=c("base","NAA", "M", "NAA + M", "NAA + M + CPI"))

df$var <- factor(df$var, levels=c("Recruitment","SSB","F"))
dfpoints <- subset(df, peel == 1:7 & Year == 2018:2012)
df$peel <- as.character(df$peel)
df$Year <- as.integer(df$Year)
dfpoints$peel <- as.character(dfpoints$peel)
dfpoints$Year <- as.integer(dfpoints$Year)
ggplot(df, aes(x=Year,y=val, color=peel, group=peel)) +
  geom_line() +
  geom_point(data=dfpoints, aes(x=Year,y=val, color=peel)) +
  geom_label(data=dfrho, aes(x=Year, y=yval, label=val), inherit.aes=F, parse=T, hjust=0, label.r=unit(0, "lines"), label.size=NA) +
  ylab(bquote(paste("Mohn's ", rho))) +
  facet_grid(cols=vars(Model), rows=vars(var)) +
  # scale_y_continuous(limits=c(-1,2)) +
  coord_cartesian(ylim=c(-1,2)) +
  theme_bw() +
  theme(legend.position = "none")
```

#### Fig 6. NAA 6-panel (base, NAA, M, NAA + M, NAA + M + CPI)

Open to suggestions on how and what to show:

- Which models?
- Time period? Currently zoomed in on last 25 years since population is at much lower levels.
- Using last F (2018) in 3-year projections. Haikun had F = 0 in projections.

```{r message=FALSE, fig.height = 5, fig.width = 10}
mod.list <- c(here("results","dat_2019","bias_correct_oe","NAA","m1.rds"),
              here("results","dat_2019","bias_correct_oe","NAA","m6.rds"),
              here("results","dat_2019","bias_correct_oe","M","m5.rds"),
              here("results","dat_2019","bias_correct_oe","NAA_M_iid","m5.rds"),
              here("results","dat_2019","bias_correct_oe","NAA_M_CPI","m22.rds"))
mods <- lapply(mod.list, readRDS)
mod.labs <- c("base","NAA", "M", "NAA + M", "NAA + M + CPI")

# mod.list <- c(here("results","dat_2019","bias_correct_oe","NAA","m1.rds"),
#               here("results","dat_2019","bias_correct_oe","NAA","m6.rds"),
#               here("results","dat_2019","bias_correct_oe","M","m5.rds"))
# mods <- lapply(mod.list, readRDS)
# mod.labs <- c("base","NAA", "M")

years <- mods[[1]]$years_full # include projections
ny <- length(years)
ny.plot <- 26
ny.cut <- ny-ny.plot
na <- mods[[1]]$env$data$n_ages
alpha <- .05 # 95% CI
df <- data.frame(matrix(NA, nrow=0, ncol=6))
colnames(df) <- c("Year","Age","val","lo","hi","Model")
for(i in 1:length(mods)){
  tmp <- summary(mods[[i]]$sdrep)
  ind <- rownames(tmp) == "log_NAA_rep"
  tmplo <- as.data.frame(exp(array(tmp[ind,1] - qnorm(0.975)*tmp[ind,2], dim = c(ny, na))))
  tmphi <- as.data.frame(exp(array(tmp[ind,1] + qnorm(0.975)*tmp[ind,2], dim = c(ny, na))))
  tmp <- as.data.frame(exp(array(tmp[ind,1], dim = c(ny, na))))
  
  colnames(tmp) <- paste0("Age_",1:na)
  tmp$Year <- years
  df.tmp <- tmp %>% tidyr::pivot_longer(-Year,
          names_to = "Age",
          names_prefix = "Age_",
          names_transform = list(Age = as.integer),
          values_to = "val")
  df.tmp$Age <- paste0("Age ",df.tmp$Age)
  df.tmp$hi <- as.vector(t(tmphi))
  df.tmp$lo <- as.vector(t(tmplo))
  df.tmp$Model <- mod.labs[i]
  df <- rbind(df, df.tmp)
}

df$Model <- factor(df$Model, levels=c("base","NAA", "M", "NAA + M", "NAA + M + CPI"), labels=c("base","NAA", "M", "NAA + M", "NAA + M + CPI"))

df[,3:5] <- df[,3:5]/10000
df$Year <- as.integer(df$Year)
df.plot <- subset(df, Year > 1993)
dat <- data.table(df.plot)
dat[,y_min := 0, by = Age]
ggplot(dat, aes(x=Year, y=val, color=Model, group=Model)) +
  geom_ribbon(aes(ymin=lo, ymax=hi, fill=Model), color=NA, alpha=.15) +
  geom_line(size=.8) +
  geom_vline(xintercept = tail(mods[[1]]$years,1), linetype=2, size=.4) +
  facet_wrap(vars(Age), scales="free_y", ncol=3, strip.position = "top") +
  ylab(expression(Numbers~at~age~(x~10^5))) +
  geom_blank(aes(y = y_min)) +
  scale_y_continuous(expand=c(0.01,0.01)) +
  coord_cartesian(xlim=c(1995,2021)) +
  scale_color_jco() +
  scale_fill_jco() +
  theme_bw() +
  theme(strip.background = element_blank(), strip.placement = "outside")

# NAA relative to base model
dat.rel <- dat %>% group_by(Year, Age) %>%
  mutate(val.rel = val/val[Model=='base']) %>% as.data.frame
  
ggplot(dat.rel, aes(x=Year, y=val.rel, color=Model, group=Model)) +
  # geom_ribbon(aes(ymin=lo, ymax=hi, fill=Model), color=NA, alpha=.15) +
  geom_line(size=.8) +
  geom_vline(xintercept = tail(mods[[1]]$years,1), linetype=2, size=.4) +
  facet_wrap(vars(Age), scales="free_y", ncol=3, strip.position = "top") +
  # ylab(expression(Numbers~at~age~(x~10^5))) +
  ylab("Relative numbers at age (to base model)") +
  geom_blank(aes(y = y_min)) +
  scale_y_continuous(expand=c(0.02,0.02)) +
  coord_cartesian(xlim=c(1995,2021)) +
  scale_color_jco() +
  scale_fill_jco() +
  theme_bw() +
  theme(strip.background = element_blank(), strip.placement = "outside")


```

#### Fig 7. SSB and F (base, NAA, M, NAA + M, NAA + M + CPI)

Point of Figs. 6-7 is to show the impact of model choice on stock status. Could show a Kobe plot instead (or addition).

```{r message=FALSE, fig.height = 5, fig.width = 7}
mod.list <- c(here("results","dat_2019","bias_correct_oe","NAA","m1.rds"),
              here("results","dat_2019","bias_correct_oe","NAA","m6.rds"),
              here("results","dat_2019","bias_correct_oe","M","m5.rds"),
              here("results","dat_2019","bias_correct_oe","NAA_M_iid","m5.rds"),
              here("results","dat_2019","bias_correct_oe","NAA_M_CPI","m22.rds"))
# mod.list <- c(here("results","dat_2019","bias_correct_oe","best_zeroFproj","m1.rds"),
#               here("results","dat_2019","bias_correct_oe","best_zeroFproj","m3.rds"),
#               here("results","dat_2019","bias_correct_oe","best_zeroFproj","m5.rds"),
#               here("results","dat_2019","bias_correct_oe","best_zeroFproj","m6.rds"),
#               here("results","dat_2019","bias_correct_oe","best_zeroFproj","m8.rds"))
mods <- lapply(mod.list, readRDS)
mod.labs <- c("base","NAA", "M", "NAA + M", "NAA + M + CPI")

# mod.list <- c(here("results","dat_2019","bias_correct_oe","NAA","m1.rds"),
#               here("results","dat_2019","bias_correct_oe","NAA","m6.rds"),
#               here("results","dat_2019","bias_correct_oe","M","m5.rds"))
# mods <- lapply(mod.list, readRDS)
# mod.labs <- c("base","NAA", "M")

years = mods[[1]]$years_full # include projections
alpha = .05 # 95% CI
df <- data.frame(matrix(NA, nrow=0, ncol=6))
colnames(df) <- c("Year","var","val","lo","hi","Model")
for(i in 1:length(mods)){
  std = summary(mods[[i]]$sdrep)
  ssb.ind <- which(rownames(std) == "log_SSB")
	log.ssb <- std[ssb.ind,1]
  ssb = exp(log.ssb)/1000
	ssb.cv <- std[ssb.ind,2]
  log.ssb.ci <- log.ssb + cbind(qnorm(1-alpha/2)*ssb.cv, -qnorm(1-alpha/2)*ssb.cv)
  ssb.ci = exp(log.ssb.ci)/1000
  df <- rbind(df, data.frame(Year=years, var="SSB", val=ssb, lo=ssb.ci[,1], hi=ssb.ci[,2], Model=mod.labs[i]))

  n_ages = mods[[i]]$env$data$n_ages
	faa.ind <- which(rownames(std) == "log_FAA_tot")
	log.faa <- matrix(std[faa.ind,1], length(years), n_ages)
	faa.cv <- matrix(std[faa.ind,2], length(years), n_ages)
	age.full.f <- apply(log.faa,1, function(x) max(which(x == max(x))))
  full.f.ind = cbind(1:length(years), age.full.f)
  log.full.f <- log.faa[full.f.ind]
  full.f.cv <- faa.cv[full.f.ind]
  log.f.ci <- log.full.f + cbind(qnorm(1-alpha/2)*full.f.cv, -qnorm(1-alpha/2)*full.f.cv)
  full.f = exp(log.full.f)
  df <- rbind(df, data.frame(Year=years, var="F", val=full.f, lo=exp(log.f.ci[,1]), hi=exp(log.f.ci[,2]), Model=mod.labs[i]))
}
df$Model <- factor(df$Model, levels=c("base","NAA", "M", "NAA + M", "NAA + M + CPI"), labels=c("base","NAA", "M", "NAA + M", "NAA + M + CPI"))
df$Year <- as.integer(df$Year)
dat <- data.table(df)
dat[,y_min := 0, by = var]

# exclude years before 1993 in dat bc ggplot doesn't recalculate y-axis limits
dat <- subset(dat, Year > 1992)

ggplot(dat, aes(x=Year, y=val, color=Model, group=Model)) +
  geom_ribbon(aes(ymin=lo, ymax=hi, fill=Model), color=NA, alpha=.15) +
  geom_line(size=.8) +
  geom_vline(xintercept = tail(mods[[1]]$years,1), linetype=2, size=.4) +
  facet_wrap(vars(var), scales="free_y", ncol=1, strip.position = "left") +
  ylab(NULL) +
  geom_blank(aes(y = y_min)) +
  scale_y_continuous(expand=c(0.01,0.01)) +
  coord_cartesian(xlim=c(1995,2021)) +
  scale_color_jco() +
  scale_fill_jco() +
  theme_bw() +
  theme(strip.background = element_blank(), strip.placement = "outside")
```

<!-- #### Fig 8. Compare projections of SSB, SSB/SSB_MSY, CPI, Recruits (base, NAA, M, NAA + M, NAA + M + CPI) -->

<!-- ```{r message=FALSE, fig.height = 5, fig.width = 7} -->
<!-- mod.list <- c(here("results","dat_2019","bias_correct_oe","NAA","m1.rds"), -->
<!--               here("results","dat_2019","bias_correct_oe","NAA","m6.rds"), -->
<!--               here("results","dat_2019","bias_correct_oe","M","m5.rds"), -->
<!--               here("results","dat_2019","bias_correct_oe","NAA_M_iid","m5.rds"), -->
<!--               here("results","dat_2019","bias_correct_oe","NAA_M_CPI","m22.rds")) -->
<!-- # mod.list <- c(here("results","dat_2019","bias_correct_oe","best_zeroFproj","m1.rds"), -->
<!-- #               here("results","dat_2019","bias_correct_oe","best_zeroFproj","m3.rds"), -->
<!-- #               here("results","dat_2019","bias_correct_oe","best_zeroFproj","m5.rds"), -->
<!-- #               here("results","dat_2019","bias_correct_oe","best_zeroFproj","m6.rds"), -->
<!-- #               here("results","dat_2019","bias_correct_oe","best_zeroFproj","m8.rds")) -->
<!-- mods <- lapply(mod.list, readRDS) -->
<!-- mod.labs <- c("base","NAA", "M", "NAA + M", "NAA + M + CPI") -->

<!-- # mod.list <- c(here("results","dat_2019","bias_correct_oe","NAA","m1.rds"), -->
<!-- #               here("results","dat_2019","bias_correct_oe","NAA","m6.rds"), -->
<!-- #               here("results","dat_2019","bias_correct_oe","M","m5.rds")) -->
<!-- # mods <- lapply(mod.list, readRDS) -->
<!-- # mod.labs <- c("base","NAA", "M") -->

<!-- n.yrs.plot = 6 -->
<!-- years = tail(mods[[1]]$years_full, n.yrs.plot) # last 3 assessment years, 3 proj years -->
<!-- alpha = .05 # 95% CI -->
<!-- df <- data.frame(matrix(NA, nrow=0, ncol=6)) -->
<!-- colnames(df) <- c("Year","var","val","lo","hi","Model") -->
<!-- for(i in 1:length(mods)){ -->
<!--   std = summary(mods[[i]]$sdrep) -->
<!--   ssb.ind <- which(rownames(std) == "log_SSB") -->
<!-- 	log.ssb <- std[ssb.ind,1] -->
<!--   ssb = tail(exp(log.ssb)/1000, n.yrs.plot) -->
<!-- 	ssb.cv <- std[ssb.ind,2] -->
<!--   log.ssb.ci <- log.ssb + cbind(qnorm(1-alpha/2)*ssb.cv, -qnorm(1-alpha/2)*ssb.cv) -->
<!--   ssb.ci = tail(exp(log.ssb.ci)/1000, n.yrs.plot) -->
<!--   df <- rbind(df, data.frame(Year=years, var="SSB", val=ssb, lo=ssb.ci[,2], hi=ssb.ci[,1], Model=mod.labs[i])) -->

<!--   cov <- mods[[i]]$sdrep$cov -->
<!--   n_years_full = length(mods[[i]]$years_full) -->
<!--   n_ages = mods[[i]]$env$data$n_ages -->
<!-- 	inds <- list(MSY = which(rownames(std) == "log_MSY")) -->
<!-- 	inds$FMSY <- which(rownames(std) == "log_FMSY") -->
<!-- 	inds$SSBMSY <- which(rownames(std) == "log_SSB_MSY") -->
<!-- 	inds$RMSY <- which(rownames(std) == "log_R_MSY") -->
<!-- 	inds$ssb <- which(rownames(std) == "log_SSB") -->
<!-- 	inds$faa <- which(rownames(std) == "log_FAA_tot") -->
<!--   log.faa <- matrix(std[inds$faa,1], n_years_full, n_ages) -->
<!--   age.full.f <- apply(log.faa,1, function(x) max(which(x == max(x)))) -->
<!--   inds$full.f <- (age.full.f-1)*n_years_full + 1:n_years_full  + min(inds$faa) - 1 #cbind(1:n_years, age.full.f) -->
<!--   log.rel.ssb.rel.F.cov <- lapply(1:n_years_full, function(x) -->
<!-- 	{ -->
<!-- 	    K <- cbind(c(1,-1,0,0),c(0,0,1,-1)) -->
<!-- 	    ind <- c(inds$ssb[x],inds$SSBMSY[x],inds$full.f[x],inds$FMSY[x]) -->
<!-- 	    tcov <- cov[ind,ind] -->
<!-- 	    return(t(K) %*% tcov %*% K) -->
<!-- 	}) -->
<!--   rel.ssb.vals <- std[inds$ssb,1][1:n_years_full] - std[inds$SSBMSY,1][1:n_years_full] -->
<!--   cv <- sapply(log.rel.ssb.rel.F.cov, function(x) return(sqrt(x[1,1]))) -->
<!--   ci <-  tail(exp(rel.ssb.vals + cbind(-qnorm(1-alpha/2)*cv, qnorm(1-alpha/2)*cv)), n.yrs.plot) -->
<!--   df <- rbind(df, data.frame(Year=years, var="SSB~/~SSB[MSY]", val=tail(exp(rel.ssb.vals), n.yrs.plot), lo=ci[,1], hi=ci[,2], Model=mod.labs[i]))   -->
<!-- } -->
<!-- df$Model <- factor(df$Model, levels=c("base","NAA", "M", "NAA + M", "NAA + M + CPI"), labels=c("base","NAA", "M", "NAA + M", "NAA + M + CPI")) -->
<!-- df$Year <- as.integer(df$Year) -->
<!-- dat <- data.table(df) -->
<!-- dat[,y_min := 0, by = var] -->

<!-- ggplot(dat, aes(x=Year, y=val, color=Model, group=Model)) + -->
<!--   geom_ribbon(aes(ymin=lo, ymax=hi, fill=Model), color=NA, alpha=.15) + -->
<!--   geom_line(size=.8) + -->
<!--   geom_vline(xintercept = tail(mods[[1]]$years,1), linetype=2, size=.4) + -->
<!--   facet_wrap(vars(var), scales="free_y", ncol=1, strip.position = "left", labeller = label_parsed) + -->
<!--   ylab(NULL) + -->
<!--   geom_blank(aes(y = y_min)) + -->
<!--   scale_y_continuous(expand=c(0.01,0.01)) + -->
<!--   # coord_cartesian(xlim=c(1995,2021)) + -->
<!--   scale_color_jco() + -->
<!--   scale_fill_jco() + -->
<!--   theme_bw() + -->
<!--   theme(strip.background = element_blank(), strip.placement = "outside") -->
<!-- ``` -->






