---
title: "2D AR1 random effects on NAA vs. M (+CPI)"
output:
  word_document: default
  html_document:
    df_print: paged
    self_contained: no
---

```{r setup, include=FALSE, cache = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi=300, dev = 'png', fig.align = 'center')
library(here)
library(wham)
library(tidyverse)
# devtools::load_all("/home/bstock/Documents/wham")
# library(kableExtra)
library(knitr)
library(ggsci)
library(data.table)
```

## Tables

`Converged` = converged with positive definite Hessian. Model in each table with **lowest retro (not AIC)** is highlighted in grey and plotted in the figures.

#### Table 1. NAA only (models where only NAA are random effects)

Model `m1`, `NAA_sigma = rec` + `NAA_cor = iid`, estimates recruitment as independent random effects with $\sigma_R$. This is closest to a SCAA model and referred to as the "base" model in figures. `NAA_sigma = rec` + `NAA_cor = ar1_y` estimates recruitment as correlated random effects (AR1 by year). `NAA_sigma = rec+1` is the 'full state-space' model with all numbers-at-age as random effects, one $\sigma_R$ for age-1 and one $\sigma_a$ for all other ages. Models `m3`-`m6` are the four in Haikun's draft.

```{r}
df.mods <- data.frame(NAA_cor = c('iid','ar1_y','iid','ar1_a','ar1_y','2dar1'),
                      NAA_sigma = c('rec','rec','rec+1','rec+1','rec+1','rec+1'), stringsAsFactors=FALSE)
n.mods <- dim(df.mods)[1]
# df.mods$Model <- paste0("m",1:n.mods)
df.mods$Model <- c("Base",paste0("NAA-",1:(n.mods-1)))
df.mods <- df.mods %>% select(Model, everything()) # moves Model to first col

# load models
mod.list <- here("results","revision2","NAA",paste0(df.mods$Model,".rds"))
# mod.list <- here("results","dat_2019","bias_correct_oe","NAA",paste0(df.mods$Model,".rds"))
mods <- lapply(mod.list, readRDS)

# calc results table
opt_conv = 1-sapply(mods, function(x) x$opt$convergence)
ok_sdrep = sapply(mods, function(x) if(x$na_sdrep==FALSE & !is.na(x$na_sdrep)) 1 else 0)
df.mods$conv <- as.logical(opt_conv)
df.mods$pdHess <- as.logical(ok_sdrep)
df.mods$runtime <- sapply(mods, function(x) x$runtime)
df.mods$NLL <- sapply(mods, function(x) round(x$opt$objective,3))
df.aic <- as.data.frame(compare_wham_models(mods, sort=FALSE, calc.rho=T, do.print=F)$tab)
df.aic$AIC[df.mods$pdHess==FALSE] <- NA
minAIC <- min(df.aic$AIC, na.rm=T)
df.aic$dAIC <- round(df.aic$AIC - minAIC,1)
df.mods <- cbind(df.mods, df.aic)
rownames(df.mods) <- NULL

# df.mods$Model <- paste0("NAA-",1:6)
tochar <- function(vec2){
  if(sum(vec2)==0){
    x <- "---"
  } else {
    x <- paste0(format(round(vec2[1],2), nsmall=2), " (", format(round(vec2[2],2), nsmall=2),")")
  }
  return(x)
}
naasig <- lapply(mods, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="NAA_sigma",], ncol=2))
df.mods$sig_R <- sapply(naasig, function(x) tochar(x[1,]))
df.mods$sig_a <- c("---","---",sapply(naasig[3:6], function(x) tochar(x[2,])))
naarho_y <- lapply(mods, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="NAA_rho_y",], ncol=2))
df.mods$rho_y <- sapply(naarho_y, function(x) tochar(x[1,]))
naarho_a <- lapply(mods, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="NAA_rho_a",], ncol=2))
df.mods$rho_a <- sapply(naarho_a, function(x) tochar(x[1,]))

# dplyr::recode(df.mods$Model, m1="NAA-1", m2="NAA-2", m3="NAA-3", m4="NAA-4", m5="NAA-5", m6="NAA-6")
# df.mods$NAA_cor <- c("---","$\\rho_{y}$","---","$\\rho_{a}$","$\\rho_{y}$","$\\rho_{a}, \\rho_{y}$")
# df.mods$NAA_sigma <- c("$\\sigma_{R}$","$\\sigma_{R}$","$\\sigma_{R}, \\sigma_{a}$","$\\sigma_{R}, \\sigma_{a}$","$\\sigma_{R}, \\sigma_{a}$","$\\sigma_{R}, \\sigma_{a}$")
df.mods <- within(df.mods, rm(NAA_cor,NAA_sigma,conv,runtime,pdHess))
df.mods <- df.mods[,c(1,8:11,2,4,3,5:7)]

# posdef = which(vign6_res$pdHess == TRUE)
thebest = which(df.mods$dAIC == 0)
df.mods %>%
  # select(-one_of("pdHess")) %>% 
  # dplyr::rename("Variance\nparameters"="NAA_sigma", "Correlation\nparameters"="NAA_cor", "$\\Delta AIC$"="dAIC",  
  #              # "Converged"="conv", "Runtime\n(min)"="runtime", 
  #               "-log$(\\mathcal{L})$"="NLL","$\\rho_{R}$"="rho_R", "$\\rho_{SSB}$"="rho_SSB", "$\\rho_{\\overline{F}}$"="rho_Fbar") %>%
  dplyr::rename("$\\sigma_R$"="sig_R", "$\\sigma_a$"="sig_a", 
               "$\\rho_{year}$"="rho_y", "$\\rho_{age}$"="rho_a",
               # "Converged"="conv", "Runtime\n(min)"="runtime", 
               "$\\Delta AIC$"="dAIC", "-log$(\\mathcal{L})$"="NLL",
               # "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{\\overline{F}}$"="rho_Fbar") %>%
               "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{F}$"="rho_Fbar") %>%
  kable(escape = F)
  # kable(escape = F) %>%
  # kable_styling(bootstrap_options = c("condensed","responsive"))
  # kable_styling(bootstrap_options = c("condensed","responsive")) %>%
  # row_spec(thebest, background = gray.colors(10,end=0.95)[10])
  # row_spec(thebest, background = gray.colors(10,end=0.95)[10]) %>%
  # row_spec(thebest, bold=TRUE)
```

---

#### Table 2. M only (models where only M is a random effect)

NAA as in `m1` above (base model $\approx$ SCAA, NOT "full state-space"). Just estimating $\mu_M$, without any random effects on NAA or M, reduces AIC and $\rho$ a lot (compare `m1` to `m6`).

```{r}
# df.mods <- data.frame(M_re = rep(c('none','iid','ar1_a','ar1_y','2dar1'),2),
#                       est_M = rep(c(FALSE,TRUE),each=5), stringsAsFactors=FALSE)
# n.mods <- dim(df.mods)[1]
# df.mods$Model <- paste0("m",1:n.mods)
df.mods <- data.frame(M_re = c('none','iid','ar1_a','ar1_y','2dar1'), stringsAsFactors=FALSE)
n.mods <- dim(df.mods)[1]
df.mods$Model <- c("Base",paste0("M-",1:(n.mods-1)))
df.mods <- df.mods %>% select(Model, everything()) # moves Model to first col

# load models
mod.list <- here("results","revision2","M",paste0(df.mods$Model,".rds"))
mods <- lapply(mod.list, readRDS)

# calc results table
opt_conv = 1-sapply(mods, function(x) x$opt$convergence)
ok_sdrep = sapply(mods, function(x) if(x$na_sdrep==FALSE & !is.na(x$na_sdrep)) 1 else 0)
df.mods$conv <- as.logical(opt_conv)
df.mods$pdHess <- as.logical(ok_sdrep)
df.mods$runtime <- sapply(mods, function(x) x$runtime)
df.mods$NLL <- sapply(mods, function(x) round(x$opt$objective,3))
df.aic <- as.data.frame(compare_wham_models(mods, sort=FALSE, calc.rho=T, do.print=F)$tab)
df.aic$AIC[df.mods$pdHess==FALSE] <- NA
minAIC <- min(df.aic$AIC, na.rm=T)
df.aic$dAIC <- round(df.aic$AIC - minAIC,1)
df.mods <- cbind(df.mods, df.aic)
rownames(df.mods) <- NULL

# df.mods$Model <- paste0("M-",1:n.mods)
tochar <- function(x){
  if(!is.null(x)){
    if(nrow(x)==0){
      y <- "---"
    } else {
      if(sum(x)==0){
        y <- "---"
      } else {
        if(x[,2] == 0){
          y <- "---"
          # y <- paste0(format(round(x[1],2), nsmall=2))
        } else {
          y <- paste0(format(round(x[1],2), nsmall=2), " (", format(round(x[2],2), nsmall=2),")")
        }
      }
    }
  } else {
    y <- "*"
  }
  return(y)
}

meanM <- lapply(mods, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="mean_M",], ncol=2))
df.mods$meanM <- sapply(meanM, function(x) tochar(x))
sigM <- lapply(mods, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="sigma_M",], ncol=2))
df.mods$sigM <- sapply(sigM, function(x) tochar(x))
Mrho_y <- lapply(mods, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="rho_M_y",], ncol=2))
df.mods$rho_y <- sapply(Mrho_y, function(x) tochar(x))
Mrho_a <- lapply(mods, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="rho_M_a",], ncol=2))
df.mods$rho_a <- sapply(Mrho_a, function(x) tochar(x))

df.mods <- within(df.mods, rm(M_re,est_M,conv,runtime,pdHess))
df.mods <- df.mods[,c(1,8:11,2,4,3,5:7)]

# thebest = which(df.mods$dAIC == 0)
# thebest = c(5,10)
# thebest = 5
df.mods %>%
  # select(-one_of("pdHess")) %>% 
  dplyr::rename("$\\sigma_M$"="sigM", "$\\mu_M$"="meanM", 
               "$\\rho_{year}$"="rho_y", "$\\rho_{age}$"="rho_a",
               # "Converged"="conv", "Runtime\n(min)"="runtime", 
               "$\\Delta AIC$"="dAIC", "-log$(\\mathcal{L})$"="NLL",
               # "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{\\overline{F}}$"="rho_Fbar") %>%
               "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{F}$"="rho_Fbar") %>%
  kable(escape = F)
  # kable(escape = F) %>%
  # kable_styling(bootstrap_options = c("condensed","responsive"))
  # kable_styling(bootstrap_options = c("condensed","responsive")) %>%
  # row_spec(thebest, background = gray.colors(10,end=0.95)[10])
  # row_spec(thebest, background = gray.colors(10,end=0.95)[10]) %>%
  # row_spec(thebest, bold=TRUE)
```

---

#### Table 3. NAA + M.

```{r}
# df.mods1 <- data.frame(M_re = rep(c('none','iid','ar1_a','ar1_y','2dar1'),2),
#                       est_M = rep(c(FALSE,TRUE),each=5), stringsAsFactors=FALSE)
# n.mods <- dim(df.mods1)[1]
# df.mods1$Model <- paste0("m",1:n.mods)
# df.mods1$NAA_re <- "2dar1"
# df.mods1 <- df.mods1 %>% select(Model, NAA_re, everything()) %>% filter(M_re %in% c("iid","2dar1"))
df.mods <- data.frame(M_re = c('iid','2dar1','iid','2dar1'),
                      NAA_cor = c('iid','iid','2dar1','2dar1'), stringsAsFactors=FALSE)
n.mods <- dim(df.mods)[1]
df.mods$Model <- paste0("NAA-M-",1:n.mods)
df.mods <- df.mods %>% select(Model, everything()) # moves Model to first col

# load models
# mod.list <- here("results","dat_2019","bias_correct_oe","NAA_M",paste0(df.mods1$Model,".rds"))
mod.list <- here("results","revision2","NAA_M",paste0(df.mods$Model,".rds"))
mods1 <- lapply(mod.list, readRDS)

tochar <- function(x){
  if(is.null(x)){
    y <- "*"
    return(y)
  } else {
    if(!is.null(x)){
      x <- matrix(x, ncol=2)
      if(nrow(x)==0){
        y <- "---"
      } else {
        if(sum(x)==0){
          y <- "---"
        } else {
          if(x[,2] == 0){
            y <- "---"
            # y <- paste0(format(round(x[1],2), nsmall=2))
          } else {
            y <- paste0(format(round(x[1],2), nsmall=2), " (", format(round(x[2],2), nsmall=2),")")
          }
        }
      }
    }
  }
  return(y)
}
extract_sdrep <- function(mod, var){
  if(mod$is_sdrep) if(!mod$na_sdrep){
      matrix(summary(mod$sdrep)[rownames(summary(mod$sdrep))==var,], ncol=2)
  } else {
    y <- NULL
  }
}

# # get NAA_re par estimates
# # naasig <- lapply(mods1, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="NAA_sigma",], ncol=2))
# naasig <- lapply(mods1, extract_sdrep, "NAA_sigma")
# # naarho_y <- lapply(mods1, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="NAA_rho_y",], ncol=2))
# naarho_y <- lapply(mods1, extract_sdrep, "NAA_rho_y")
# # naarho_a <- lapply(mods1, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="NAA_rho_a",], ncol=2))
# naarho_a <- lapply(mods1, extract_sdrep, "NAA_rho_a")
# df.mods1$sig_R <- sapply(naasig, function(x) tochar(x[1,]))
# df.mods1$sig_a <- sapply(naasig, function(x) tochar(x[2,]))
# df.mods1$rho_y <- sapply(naarho_y, function(x) tochar(x))
# df.mods1$rho_a <- sapply(naarho_a, function(x) tochar(x))
# 
# # get M_re par estimates
# meanM <- lapply(mods1, extract_sdrep, "mean_M")
# sigM <- lapply(mods1, extract_sdrep, "sigma_M")
# Mrho_y <- lapply(mods1, extract_sdrep, "rho_M_y")
# Mrho_a <- lapply(mods1, extract_sdrep, "rho_M_a")
# # meanM <- lapply(mods1, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="mean_M",], ncol=2))
# df.mods1$meanM <- sapply(meanM, function(x) tochar(x))
# # sigM <- lapply(mods1, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="sigma_M",], ncol=2))
# df.mods1$sigM <- sapply(sigM, function(x) tochar(x))
# # Mrho_y <- lapply(mods1, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="rho_M_y",], ncol=2))
# df.mods1$Mrho_y <- sapply(Mrho_y, function(x) tochar(x))
# # Mrho_a <- lapply(mods1, function(x) matrix(summary(x$sdrep)[rownames(summary(x$sdrep))=="rho_M_a",], ncol=2))
# df.mods1$Mrho_a <- sapply(Mrho_a, function(x) tochar(x))
# 
# # correct * vs. ---
# df.mods1$meanM[2] = "---"
# df.mods1$Mrho_y[3] = df.mods1$Mrho_a[3] = "---"

# # calc results table
# opt_conv = 1-sapply(mods1, function(x) x$opt$convergence)
# ok_sdrep = sapply(mods1, function(x) if(x$na_sdrep==FALSE & !is.na(x$na_sdrep)) 1 else 0)
# df.mods1$conv <- as.logical(opt_conv)
# df.mods1$pdHess <- as.logical(ok_sdrep)
# df.mods1$runtime <- sapply(mods1, function(x) x$runtime)
# df.mods1$NLL <- sapply(mods1, function(x) round(x$opt$objective,3))
# df.aic <- as.data.frame(compare_wham_models(mods1, sort=FALSE, calc.rho=T, do.print=F)$tab)
# df.aic$AIC[df.mods1$pdHess==FALSE] <- NA
# minAIC <- min(df.aic$AIC, na.rm=T)
# df.aic$dAIC <- round(df.aic$AIC - minAIC,1)
# df.mods1 <- cbind(df.mods1, df.aic)
# rownames(df.mods1) <- NULL

# calc results table
opt_conv = 1-sapply(mods1, function(x) x$opt$convergence)
ok_sdrep = sapply(mods1, function(x) if(x$na_sdrep==FALSE & !is.na(x$na_sdrep)) 1 else 0)
df.mods$conv <- as.logical(opt_conv)
df.mods$pdHess <- as.logical(ok_sdrep)
df.mods$runtime <- sapply(mods1, function(x) x$runtime)
df.mods$NLL <- sapply(mods1, function(x) round(x$opt$objective,3))
df.aic <- as.data.frame(compare_wham_models(mods1, sort=FALSE, calc.rho=T, do.print=F)$tab)
df.aic$AIC[df.mods$pdHess==FALSE] <- NA
minAIC <- min(df.aic$AIC, na.rm=T)
df.aic$dAIC <- round(df.aic$AIC - minAIC,1)
df.mods <- cbind(df.mods, df.aic)
rownames(df.mods) <- NULL

# # --------------------------------------------------------------------------------------------
# df.mods2 <- data.frame(M_re = rep(c('none','iid','ar1_a','ar1_y','2dar1'),2),
#                       est_M = rep(c(FALSE,TRUE),each=5), stringsAsFactors=FALSE)
# n.mods <- dim(df.mods2)[1]
# df.mods2$Model <- paste0("m",1:n.mods)
# df.mods2$NAA_re <- "iid"
# df.mods2 <- df.mods2 %>% select(Model, NAA_re, everything()) %>% filter(M_re %in% c("iid","2dar1"))
# 
# # load models
# mod.list <- here("results","dat_2019","bias_correct_oe","NAA_M_iid",paste0(df.mods2$Model,".rds"))
# mods2 <- lapply(mod.list, readRDS)

# # get NAA_re par estimates
# naasig <- lapply(mods2, extract_sdrep, "NAA_sigma")
# naarho_y <- lapply(mods2, extract_sdrep, "NAA_rho_y")
# naarho_a <- lapply(mods2, extract_sdrep, "NAA_rho_a")
# df.mods2$sig_R <- sapply(naasig, function(x) tochar(x[1,]))
# df.mods2$sig_a <- sapply(naasig, function(x) tochar(x[2,]))
# df.mods2$rho_y <- sapply(naarho_y, function(x) tochar(x))
# df.mods2$rho_a <- sapply(naarho_a, function(x) tochar(x))
# 
# # get M_re par estimates
# meanM <- lapply(mods2, extract_sdrep, "mean_M")
# sigM <- lapply(mods2, extract_sdrep, "sigma_M")
# Mrho_y <- lapply(mods2, extract_sdrep, "rho_M_y")
# Mrho_a <- lapply(mods2, extract_sdrep, "rho_M_a")
# df.mods2$meanM <- sapply(meanM, function(x) tochar(x))
# df.mods2$sigM <- sapply(sigM, function(x) tochar(x))
# df.mods2$Mrho_y <- sapply(Mrho_y, function(x) tochar(x))
# df.mods2$Mrho_a <- sapply(Mrho_a, function(x) tochar(x))
# 
# # correct * vs. ---
# df.mods2$rho_y[3] = df.mods2$rho_a[3] = "---"
# df.mods2$meanM[2] = "---"
# df.mods2$Mrho_y[3] = df.mods2$Mrho_a[3] = "---"

# # calc results table
# opt_conv = 1-sapply(mods2, function(x) x$opt$convergence)
# ok_sdrep = sapply(mods2, function(x) if(x$na_sdrep==FALSE & !is.na(x$na_sdrep)) 1 else 0)
# df.mods2$conv <- as.logical(opt_conv)
# df.mods2$pdHess <- as.logical(ok_sdrep)
# df.mods2$runtime <- sapply(mods2, function(x) x$runtime)
# df.mods2$NLL <- sapply(mods2, function(x) round(x$opt$objective,3))
# df.aic <- as.data.frame(compare_wham_models(mods2, sort=FALSE, calc.rho=T, do.print=F)$tab)
# df.aic$AIC[df.mods2$pdHess==FALSE] <- NA
# minAIC <- min(df.aic$AIC, na.rm=T)
# df.aic$dAIC <- round(df.aic$AIC - minAIC,1)
# df.mods2 <- cbind(df.mods2, df.aic)
# rownames(df.mods2) <- NULL

# -----------------------------------------------------------
# combine two tables
# df.mods <- rbind(df.mods2, df.mods1)
# df.mods$Model <- paste0("NAA-M-",1:dim(df.mods)[1])
df.mods[df.mods$pdHess==FALSE, c("NLL","dAIC","AIC","rho_R","rho_SSB","rho_Fbar")] = NA
minAIC <- min(df.mods$AIC, na.rm=T)
df.mods$dAIC <- df.mods$AIC - minAIC
# df.mods <- within(df.mods, rm(NAA_re,M_re,est_M,conv,runtime,pdHess))
df.mods <- within(df.mods, rm(conv,runtime,pdHess))
# df.mods <- df.mods[,c(1,8:11,2,4,3,5:7)]
df.mods$NLL <- paste0(format(round(df.mods$NLL,3), nsmall=3))
df.mods$dAIC <- paste0(format(round(df.mods$dAIC,1), nsmall=1))
df.mods[is.na(df.mods)] = ""
df.mods[df.mods == "       NA"] = ""
df.mods[df.mods == "  NA"] = ""
df.mods[df.mods == "iid"] = "IID"
df.mods[df.mods == "2dar1"] = "2D AR1"
df.mods[df.mods == FALSE] = "No"
df.mods[df.mods == TRUE] = "Yes"
# df.mods <- df.mods[,c(1:5,7,6,8:10)]
df.mods <- df.mods[,c(1,3,2,4:9)]

# thebest = which(df.mods$dAIC == 0)
# thebest = c(2,5)
# thebest = 2
df.mods %>%
  # select(-one_of("pdHess")) %>% 
  # dplyr::rename("$\\sigma_R$"="sig_R", "$\\sigma_a$"="sig_a", 
  #              "$\\rho_{year}$"="rho_y", "$\\rho_{age}$"="rho_a",
  #              "$\\sigma_M$"="sigM", "$\\mu_M$"="meanM", 
  #              "$\\rho^M_{year}$"="Mrho_y", "$\\rho^M_{age}$"="Mrho_a",
  #              # "Converged"="conv", "Runtime\n(min)"="runtime", 
  #              "$\\Delta AIC$"="dAIC", "-log$(\\mathcal{L})$"="NLL",
  #              "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{\\overline{F}}$"="rho_Fbar") %>%
  # dplyr::rename("Estimate $\\mu_{M}$"="est_M","Random effects\nNAA"="NAA_re","Random effects\nM"="M_re",
  #              "$\\Delta AIC$"="dAIC", "-log$(\\mathcal{L})$"="NLL",
  #              "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{\\overline{F}}$"="rho_Fbar") %>%
  # dplyr::rename("Estimate $\\mu_{M}$"="est_M","Random effects\nNAA"="NAA_re","Random effects\nM"="M_re",
  #              "$\\Delta AIC$"="dAIC", "-log$(\\mathcal{L})$"="NLL",
  #              "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{F}$"="rho_Fbar") %>%
  dplyr::rename("Random effects NAA"="NAA_cor","Random effects M"="M_re",
               "$\\Delta AIC$"="dAIC", "-log$(\\mathcal{L})$"="NLL",
               "Mohn's $\\rho_{R}$"="rho_R", "Mohn's $\\rho_{SSB}$"="rho_SSB", "Mohn's $\\rho_{F}$"="rho_Fbar") %>%
  kable(escape = F)
  # kable(escape = F) %>%
  # kable_styling(bootstrap_options = c("condensed","responsive"))
  # kable_styling(bootstrap_options = c("condensed","responsive")) %>%
  # row_spec(thebest, background = gray.colors(10,end=0.95)[10])
  # row_spec(thebest, background = gray.colors(10,end=0.95)[10]) %>%
  # row_spec(thebest, bold=TRUE)
```

---

#### Table 5. Best models, compare SSB predictions.

```{r}
df.mods <- data.frame(NAA_cor = c('iid','iid','2dar1','iid','iid','iid','2dar1'),
                      NAA_sigma = c('rec','rec+1','rec+1','rec','rec','rec+1','rec+1'),
                      M_re = c('none','none','none','iid','2dar1','2dar1','iid'), stringsAsFactors=FALSE)
n.mods <- dim(df.mods)[1]
df.mods$Model <- paste0("m",1:n.mods)
df.mods$lab <- c("Base","NAA-2","NAA-5","M-1","M-4","NAA-M-2","NAA-M-3")
df.mods <- df.mods %>% select(Model, lab, everything()) # moves Model to first col

# load models
# mod.list <- here("results","revision2","best",paste0(df.mods$Model,"_proj.rds"))
mod.list <- list("/home/bstock/Documents/ms/2D-AR1-survival/results/revision2/NAA/Base.rds",
  "/home/bstock/Documents/ms/2D-AR1-survival/results/revision2/NAA/NAA-2.rds",
  "/home/bstock/Documents/ms/2D-AR1-survival/results/revision2/NAA/NAA-5.rds",
  "/home/bstock/Documents/ms/2D-AR1-survival/results/revision2/M/M-1.rds",
  "/home/bstock/Documents/ms/2D-AR1-survival/results/revision2/M/M-4.rds",
  "/home/bstock/Documents/ms/2D-AR1-survival/results/revision2/NAA_M/NAA-M-2.rds",
  "/home/bstock/Documents/ms/2D-AR1-survival/results/revision2/NAA_M/NAA-M-3.rds")
mods <- lapply(mod.list, readRDS)

# calc results table
opt_conv = 1-sapply(mods, function(x) x$opt$convergence)
ok_sdrep = sapply(mods, function(x) if(x$na_sdrep==FALSE & !is.na(x$na_sdrep)) 1 else 0)
df.mods$conv <- as.logical(opt_conv)
df.mods$pdHess <- as.logical(ok_sdrep)
df.mods$runtime <- sapply(mods, function(x) x$runtime)
df.mods$NLL <- sapply(mods, function(x) round(x$opt$objective,3))
have_peels <- sapply(mods, function(x) !is.null(x$peels))
df.aic <- as.data.frame(compare_wham_models(mods, sort=FALSE, calc.rho=F, do.print=F)$tab)
df.aic$dAIC <- df.aic$rho_Fbar <- df.aic$rho_SSB <- df.aic$rho_R <- NA
if(any(have_peels)){
	tmp <- as.data.frame(compare_wham_models(mods[have_peels], sort=FALSE, calc.rho=T, do.print=F)$tab)
	df.aic[have_peels==TRUE, 3:5] <- tmp[,3:5]
	df.aic[df.mods$pdHess==FALSE,] <- NA
}
minAIC <- min(df.aic$AIC, na.rm=T)
df.aic$dAIC <- round(df.aic$AIC - minAIC,1)
df.mods <- cbind(df.mods, df.aic)
rownames(df.mods) <- NULL

df <- df.mods
df$Model <- df.mods$lab
# df$CPI_how <- as.character(df$CPI_how)
df[df == "0"] = "---"
df$dAIC[df$dAIC == "---"] = "0.0"
df[df == "2"] = "Yes"
df[df == "none"] = "---"
df[df == "rec"] = "Recruit"
df[df == "rec+1"] = "All NAA"
df[df == "iid"] = "IID"
df[df == "2dar1"] = "2D AR1"
df[df == FALSE] = "No"
# df$dAIC[3] = "0.0"
df[df == TRUE] = "Yes"
# df <- df[,c(1:10,12,11,13:15)]

get_proj_SSB_CI <- function(mod){
  temp = summary(mod$sdrep)
  temp = temp[rownames(temp) == "log_SSB",]
  temp = exp(cbind(temp, temp[,1] + qnorm(0.975)*cbind(-temp[,2],temp[,2])))
  temp = cbind(temp, temp[,4] - temp[,3])
  temp = tail(temp,3)
  y <- apply(temp, 1, function(x) paste0(format(round(x[1],0), nsmall=0), " (", format(round(x[3],0), nsmall=0),", ",format(round(x[4],0), nsmall=0),")"))
  names(y) = NULL
  return(y)
}
proj.SSB <- lapply(mods, get_proj_SSB_CI)
ssb.df <- do.call(rbind, proj.SSB)
df <- cbind(df, ssb.df)
colnames(df)[15:17] <- c("2019","2020","2021")

df %>%
  select(-one_of("pdHess","conv","lab")) %>%
  dplyr::rename("NAA dev"="NAA_sigma","NAA cor"="NAA_cor",
         "$\\Delta AIC$"="dAIC","$\\rho_{R}$"="rho_R", "$\\rho_{SSB}$"="rho_SSB", "$\\rho_{F}$"="rho_Fbar") %>%
kable(escape = F)

```
